A multi-dimensional extension of the Lightweight Temporal Compression method

### 2018-11-21 paper.tex
Fixed the presentation of latency results

\begin{table}
    \begin{subfigure}{\columnwidth}
    \centering
    \begin{tabular}{l|l|l|l|l}
    \hline
    \rowcolor{headcolor}
                           & \multicolumn{2}{c|}{Infinity} & \multicolumn{2}{c}{Euclidean}\\ \hline
    $\epsilon$  (mg)          & 48.8         & 34.5       & 48.8       & 34.5 \\
    Max error   (mg)          & 48.8         & 34.4       & 48.8       & 34.5 \\
    Compression ratio (\%)    & 79.77        & 72.59      & 77.49      & 70.96\\
    Peak memory   (B)         & 80           & 80         & 688        & 688  \\
    Processing time (ms)      & 0.101        & 0.094      & 0.456      & 0.406\\ \hline
    \end{tabular}
    \caption{Short biceps curl (2D)}
    \end{subfigure}\\
    \begin{subfigure}{\columnwidth}
    \centering
    \begin{tabular}{l|l|l|l|l}
    \hline
    \rowcolor{headcolor}
                   & \multicolumn{2}{c|}{Infinity} & \multicolumn{2}{c}{Euclidean} \\ \hline
    $\epsilon$ (mg)            & 48.8        & 34.5       & 48.8        & 34.5    \\
    Max error  (mg)            & 48.8        & 34.5       & 48.8        & 34.5             \\
    Compression ratio (\%)     & 77.46       & 70.98      & 75.77       & 68.81           \\
    Peak memory  (B)           & 80          & 80         & 2512        & 2608             \\
    Processing time (ms)       & 6.06        & 5.84       & 33.84       & 31.07           \\ \hline
    \end{tabular}
    \caption{Long biceps curl (2D)}
    \end{subfigure}\\
    \begin{subfigure}{\columnwidth}
    \centering
    \begin{tabular}{l|l|l|l|l}
    \hline
    \rowcolor{headcolor}
                           & \multicolumn{2}{c|}{Infinity} & \multicolumn{2}{c}{Euclidean} \\ \hline
    $\epsilon$ (mg)        & 48.8          & 28.2          & 48.8   & 28.2   \\
    Max error  (mg)        & 48.8          & 28.2          & 48.8   & 28.2   \\
    Compression ratio (\%) & 78.14         & 66.39         & 74.39  & 63.13   \\
    Peak memory (B)        & 112           & 112           & 1744   & 784    \\
    Processing time (ms)   & 0.147         & 0.134         & 0.731  & 0.514  \\ \hline
    \end{tabular}
    \caption{Short biceps curl (3D)}
    \end{subfigure}\\
    \begin{subfigure}{\columnwidth}
    \centering
    \begin{tabular}{l|l|l|l|l}
    \hline
    \rowcolor{headcolor}
                              & \multicolumn{2}{c|}{Infinity} & \multicolumn{2}{c}{Euclidean} \\ \hline
    $\epsilon$ (mg)                & 48.8        & 28.2       & 48.8     & 28.2    \\
    Max error  (mg)                & 48.8        & 28.2       & 48.8     & 28.2    \\
    Compression ratio (\%)         & 71.23       & 58.11      & 67.35    & 53.24   \\
    Peak memory (B)                & 112         & 112        & 4752     & 3856    \\
    Processing time (ms)           & 7.87        & 7.22       & 41.29    & 39.04   \\ \hline
    \end{tabular}
    \caption{Long biceps curl (3D)}
    \end{subfigure}
    \caption{Results from Experiment 1}
    \label{table:results-validation}
\end{table}

@@

We measured energy consumption associated with the transmission of
these time-series by
``replaying" the time-series after loading them as a byte array in
Neblina. We measured the current every 500~ms.

 Results are reported in Table~\ref{table:results-energy}. For a given
 $\epsilon$ and norm, the compression ratio is larger for walking than
 for running. The ratio of saved energy is relative to the reference
 current of 3.47~mA measured when Neblina transmits data without
 compression. In all cases, activating compression saves energy. The
 reduction in energy consumption behaves as the compression ratio: it
 increases with $\epsilon$,
it is higher for the infinity norm than for the Euclidean, and it is
higher for the walking activity than for running. For a realistic error
of $\epsilon$=9.8~mg, the ratio of saved energy with the infinity norm is
close to 20\% for the walking activity, which is substantial. We also
measured processing times of both infinity norm and Euclidean norm in
Neblina.The result is reported in Table~\ref{table:result-latency}.
In Neblina, the processing time of different data are similar in Infinity
norm. In Euclidean norm, the processing time is longer, and data with slight changes using more processing time with comparing result of walking data and running data.
\begin{table}[]
   \begin{subfigure}{\columnwidth}
   \centering
   \begin{tabular}{l|l|l|l|l|l|l}
   \hline
   \rowcolor{headcolor}
                          & \multicolumn{3}{c|}{Infinity} & \multicolumn{3}{c}{Euclidean} \\\hline
   $\epsilon$ (mg)             & 48.8       & 9.8      & 4.9       & 48.8      & 9.8       & 4.9    \\
   Max error (mg)              & 48.8     & 9.8        & 4.9      & 48.8   & 9.8   & 4.9  \\
   Compr.      ratio (\%)      & 88.9    & 66.4  & 45.5   & 87.6   & 63.3   & 37.2 \\
   Average (mA)                & 2.64     & 2.79   & 3.02   & 3.10    & 3.02    & 3.13  \\
   Saved energy (\%)              & 23.9    & 19.7  & 13.0  &  10.7   & 13.0   & 9.7\\
   \hline
   \end{tabular}
   \caption{Walking}
   \end{subfigure}
   \begin{subfigure}{\columnwidth}
   \centering
   \begin{tabular}{l|l|l|l|l|l|l}
   \hline
   \rowcolor{headcolor}

                     & \multicolumn{3}{c|}{Infinity} & \multicolumn{3}{c}{Euclidean} \\\hline
   $\epsilon$ (mg)        & 48.8       & 9.8      & 4.9       & 48.8      & 9.8    & 4.9    \\
   Max error (mg)         & 48.8       & 9.8      & 4.9       & 48.8      & 9.8    & 4.9   \\
   Compr.      ratio (\%) & 68.6       & 25.5     & 9.5       & 64.4      & 19.8   & 5.7   \\
   Average (mA)        & 2.88     & 3.22   & 3.38     & 2.95    & 3.32    & 3.39   \\
   Saved energy (\%)      & 17.0    & 7.2    & 2.5   & 14.9   & 4.3   & 2.2\\
   \hline
   \end{tabular}
   \caption{Running}
   \end{subfigure}
   \caption{Results from Experiment 2}
   \label{table:results-energy}
\end{table}

\begin{table}[]
    \begin{tabular}{l|l|l|l|l}
    \hline
    \rowcolor{headcolor}
                                 & \multicolumn{2}{l}{Infinity Norm} & \multicolumn{2}{l}{Euclidean Norm} \\\hline
    Data set                     & walking         & running         & walking          & running \\
    Max processing Time (μs)     & 60              & 60              & 1530             & 840     \\
    average processing Time (μs) & 30.57           & 30.040          & 144.6            & 64.34   \\       
    \hline
    \end{tabular}
    \caption{Processing time from Experiment 2}
    \label{table:result-latency}
\end{table}
%~ and the battery usage 
%~ would not change too much, because it contains others fusion method 
%~ which will running when turning on the Neblina. In 50Hz sensor sampling 
%~ rate, the average usage electric current for transmit accelerometer 
%~ data is 2.0mA. It means Neblina could transmit accelerometer data 
%~ constantly in 100/2.0=50 hours. when Neblina does not move, the average 
%~ usage electric current using Infinity norm compression is 1.95mA.

 %~ It 
%~ just extend Neblina work life about 1.28 hours. But in 200Hz sampling 
%~ rate. The electric before and after compression are 3.5 and 2.9 
%~ respectively. The running time of Neblina would be extended about 5.9 
%~ hours.

%~ We also measured the compression latency on Neblina for this experiment.
%~ The maximal measured latency was 7.56~ms, obtained for the Euclidean distance 
%~ on the walk data, finish this if the correct values are avail.

>>>>

\begin{table}
    \begin{subfigure}{\columnwidth}
    \centering
    \begin{tabular}{l|l|l|l|l}
    \hline
    \rowcolor{headcolor}
                           & \multicolumn{2}{c|}{Infinity} & \multicolumn{2}{c}{Euclidean}\\
    \rowcolor{headcolor}
    $\epsilon$  (mg)          & 48.8         & 34.5       & 48.8       & 34.5 \\
    \hline
    Max error   (mg)          & 48.8         & 34.4       & 48.8       & 34.5 \\
    Compression ratio (\%)    & 79.77        & 72.59      & 77.49      & 70.96\\
    Peak memory   (B)         & 80           & 80         & 688        & 688  \\
    Processing time (ms)      & 0.101        & 0.094      & 0.456      & 0.406\\ \hline
    \end{tabular}
    \caption{Short biceps curl (2D)}
    \end{subfigure}\\
    \begin{subfigure}{\columnwidth}
    \centering
    \begin{tabular}{l|l|l|l|l}
    \hline
    \rowcolor{headcolor}
                   & \multicolumn{2}{c|}{Infinity} & \multicolumn{2}{c}{Euclidean} \\
    \rowcolor{headcolor}
    $\epsilon$ (mg)            & 48.8        & 34.5       & 48.8        & 34.5    \\
    \hline
    Max error  (mg)            & 48.8        & 34.5       & 48.8        & 34.5             \\
    Compression ratio (\%)     & 77.46       & 70.98      & 75.77       & 68.81           \\
    Peak memory  (B)           & 80          & 80         & 2512        & 2608             \\
    Processing time (ms)       & 6.06        & 5.84       & 33.84       & 31.07           \\ \hline
    \end{tabular}
    \caption{Long biceps curl (2D)}
    \end{subfigure}\\
    \begin{subfigure}{\columnwidth}
    \centering
    \begin{tabular}{l|l|l|l|l}
    \hline
    \rowcolor{headcolor}
                           & \multicolumn{2}{c|}{Infinity} & \multicolumn{2}{c}{Euclidean} \\
    \rowcolor{headcolor}
    $\epsilon$ (mg)        & 48.8          & 28.2          & 48.8   & 28.2   \\
    \hline
    Max error  (mg)        & 48.8          & 28.2          & 48.8   & 28.2   \\
    Compression ratio (\%) & 78.14         & 66.39         & 74.39  & 63.13   \\
    Peak memory (B)        & 112           & 112           & 1744   & 784    \\
    Processing time (ms)   & 0.147         & 0.134         & 0.731  & 0.514  \\ \hline
    \end{tabular}
    \caption{Short biceps curl (3D)}
    \end{subfigure}\\
    \begin{subfigure}{\columnwidth}
    \centering
    \begin{tabular}{l|l|l|l|l}
    \hline
    \rowcolor{headcolor}
                              & \multicolumn{2}{c|}{Infinity} & \multicolumn{2}{c}{Euclidean} \\
    \rowcolor{headcolor}
    $\epsilon$ (mg)                & 48.8        & 28.2       & 48.8     & 28.2    \\
    \hline
    Max error  (mg)                & 48.8        & 28.2       & 48.8     & 28.2    \\
    Compression ratio (\%)         & 71.23       & 58.11      & 67.35    & 53.24   \\
    Peak memory (B)                & 112         & 112        & 4752     & 3856    \\
    Processing time (ms)           & 7.87        & 7.22       & 41.29    & 39.04   \\ \hline
    \end{tabular}
    \caption{Long biceps curl (3D)}
    \end{subfigure}
    \caption{Results from Experiment 1}
    \label{table:results-validation}
\end{table}

@@

We measured energy consumption associated with the transmission of 
these time-series by ``replaying" the time-series after loading them as 
a byte array in Neblina. We measured the current every 500~ms. We also 
measured the max and average latency resulting from compression in the 
data stream.

 Results are reported in Table~\ref{table:results-energy}. For a given
 $\epsilon$ and norm, the compression ratio is larger for walking than
 for running. The ratio of saved energy is relative to the reference
 current of 3.47~mA measured when Neblina transmits data without
 compression. In all cases, activating compression saves energy. The 
 reduction in energy consumption behaves as the compression ratio: it 
 increases with $\epsilon$, it is higher for the infinity norm than for 
 the Euclidean, and it is higher for the walking activity than for 
 running. For a realistic error of $\epsilon$=9.8~mg, the ratio of 
 saved energy with the infinity norm is close to 20\% for the walking 
 activity, which is substantial. Latency is higher for walking 
 than for running, and it is also higher for the Euclidean norm than 
 for the infinity norm. In all cases, the latency remains lower 
 than the 5-ms tolerable latency at 200~Hz, which demonstrates the 
 feasibility of 3D LTC compression.

\begin{table}[]
   \begin{subfigure}{\columnwidth}
   \centering
   \begin{tabular}{l|l|l|l|l|l|l}
   \hline
   \rowcolor{headcolor}
                          & \multicolumn{3}{c|}{Infinity} & \multicolumn{3}{c}{Euclidean} \\
   \rowcolor{headcolor}
   $\epsilon$ (mg)             & 48.8    & 9.8      & 4.9   & 48.8   & 9.8   & 4.9   \\
   \hline
   Max error (mg)              & 48.8    & 9.8      & 4.9   & 48.8   & 9.8   & 4.9   \\
   Compr.      ratio (\%)      & 88.9    & 66.4     & 45.5  & 87.6   & 63.3  & 37.2  \\
   Average (mA)                & 2.64    & 2.79     & 3.02  & 3.10   & 3.02  & 3.13  \\
   Saved energy (\%)           & 23.9    & 19.7     & 13.0  &  10.7  & 13.0  & 9.7   \\
   Max latency ($\mu$s)& 60      & --       & --    & 1530   & --    & --    \\
   Average latency ($\mu$s) & 31 & --       & --    & 145    & --    & --    \\    
   \hline
   \end{tabular}
   \caption{Walking}
   \end{subfigure}
   \begin{subfigure}{\columnwidth}
   \centering
   \begin{tabular}{l|l|l|l|l|l|l}
   \hline
   \rowcolor{headcolor}

                     & \multicolumn{3}{c|}{Infinity} & \multicolumn{3}{c}{Euclidean} \\
    \rowcolor{headcolor}
   $\epsilon$ (mg)        & 48.8       & 9.8      & 4.9       & 48.8      & 9.8    & 4.9    \\
   \hline
   Max error (mg)         & 48.8       & 9.8      & 4.9       & 48.8      & 9.8    & 4.9   \\
   Compr.      ratio (\%) & 68.6       & 25.5     & 9.5       & 64.4      & 19.8   & 5.7   \\
   Average (mA)        & 2.88     & 3.22   & 3.38     & 2.95    & 3.32    & 3.39   \\
   Saved energy (\%)      & 17.0    & 7.2    & 2.5   & 14.9   & 4.3   & 2.2\\
   Max latency ($\mu$s)& 60      & --       & --    & 840   & --    & --    \\
   Average latency ($\mu$s) & 30 & --       & --    & 64    & --    & --    \\    
   \hline
   \end{tabular}
   \caption{Running}
   \end{subfigure}
   \caption{Results from Experiment 2}
   \label{table:results-energy}
\end{table}
